---
title: "Homework 7"
output: pdf_document
---

\begin{center}
Earle Aguilar \\
804501476 \\
2017-02-24
\end{center}



```{r, echo=F}
library(readxl)

```

\section{7.21}
\section{8.11}
```{r}
df <- read_excel("~/vmshare/stats 101b datasets/CH 8 (P11).xlsx")

```
\subsection{a}
If the design generators are $I=ACE$ and $I=BDE$ then $D=BE$ and $E=AC$.

```{r}
design <- df[,1:5]
names(design) <- c("A","B","C","D", "E")

all((design$A*design$C) == design$E)
all((design$B * design$E) == design$D)
```

\subsection{b}

\textbf{Complete Defining Relation:} $$I = ACE = BDE = ABCD$$


\begin{center}
\begin{tabular}{| l | l | l | l | l | l | l |}
  \hline
    $A$ & $A*ACE =CE$    & $A*BDE =ABDE$ & $A*ABCD=CBD$ \\ \hline
    $B$ & $B*ACE = ABCE$ & $B*BDE = DE$  & $B*ABCD= ACD$  \\ \hline
    $C$ & $C*ACE =AE$    & $C*BDE =BCDE$ & $C*ABCD=ABD$ \\ \hline
    $D$ & $D*ACE =ACDE$  & $D*BDE =BE$   & $D*ABCD=ACB$ \\ \hline
    $E$ & $E*ACE = AC$   & $E*BDE = BD$  & $E*ABCD= ABCDE$ \\ \hline
    $AB$& $AB*ACE=BCE$   & $AB*BDE = ADE$& $AB*ABCD=CD$ \\ \hline
    $AD$& $AD*ACE=CDE$   & $AD*BDE=ABE$  & $AD*ABCD=BC$ \\ \hline
\end{tabular} 
\end{center}

\subsection{c}
```{r}
design$Yield <- df$Yield
m <- lm(Yield ~ A + B + C + D + E, design)
```
\subsection{d}
\subsection{e}

\section{8.23}
\section{8.37}
\section{8.39}
\section{8.48}