---
title: "Statistics 101B HW2"
output: pdf_document
---

\begin{center}
Earle Aguilar \\
804501476 \\
01-20-2017
\end{center}

\section{2.10}
\textbf{a.} $$\frac{11.5}{SE}=1.88$$ $$SE = 6.12$$
\textbf{b.} This is a two-sided t-test. \newline
\textbf{c.} We fail to reject the null hypothesis because $$0.0723> 0.05$$. \newline
\textbf{d.} We know: $$t_{0.975,24} = 2.063$$. Confidence interval: 
$$11.5 \pm 2.063*6.12 = [-1.13, 24.13]$$

\section{2.15}
\textbf{a.} We can reject the null hypothesis $$0.001 < 0.05$$
\textbf{b.} This is a two-sided t-test. $$2*P(t \le -3.47) = 0.001$$
\textbf{c.} $$t = \frac{ (50.19-52.52)-2 }{2.1277 \sqrt{ \frac{1}{20} + \frac{1}{20} } }$$
$$t = -6.44$$
Rejection regions: 
$$t > 2.02 \ \ or \ \ t < -2.02$$
We reject the null since $$-6.44 < -2.02$$
\textbf{d.} We reject the null. We only have to check the lower t value -2.02. \newline
\textbf{e.} $$Confidence \ \ Interval: \ \ -2.33 \pm 2.02*2.13\sqrt{\frac{1}{20} + \frac{1}{20} }$$
$$Confidence \ \ Interval: \ \ [-3.69, -0.97]$$
\textbf{f.} $$p-value \ =  7.105286*10^{-08}$$

\section{2.24}
\textbf{a.}
$$H_0: \mu_1 - \mu_2 = 0$$
$$H_1: \mu_1 - \mu_2 \ne 0$$
\textbf{b.}

```{r}
machine1 <- c(16.03, 16.01, 16.04, 15.96, 16.05, 15.98, 16.05, 16.02, 16.02, 15.99)

machine2 <- c(16.02, 16.03, 15.97, 16.04, 15.96, 16.02, 16.01, 16.01, 15.99, 16.00)

n <- 10

mean_m1 <- mean(machine1)
mean_m2 <- mean(machine2)

z <- (mean_m1 - mean_m2) / sqrt( (0.015)^2/n + (0.018)^2/n ) 
z
```
Rejection regions:
$$z > 1.96 \ \ or \ \ z < -1.96$$
We fail to reject the null since $$1.35 < 1.96$$
\textbf{c.}
```{r}
pnorm(1.35)
```
\textbf{d.}
```{r}
lb <- 0.01 - 1.96 * sqrt(((0.015)^2 + (0.018)^2 ) / 10)
ub <- 0.01 + 1.96 * sqrt(((0.015)^2 + (0.018)^2 ) / 10)
c(lb,ub)
```

\newpage

\section{2.33}
```{r, echo=F}
pairs <- 1:10

Birth_order1 <- c(6.08, 6.22, 7.99, 7.44, 6.48, 7.99, 6.32, 7.60, 6.03, 7.52)
Birth_order2 <- c(5.73, 5.80, 8.42, 6.84, 6.43, 8.76, 6.32, 7.62, 6.59, 7.67)

df <- data.frame(pairs, Birth_order1, Birth_order2)

```
\textbf{a.}
```{r}
qqnorm(df$Birth_order1-df$Birth_order2)
qqline(df$Birth_order1-df$Birth_order2)
```
The normal probability plot shows that the distributions of the differences are approximately normal.

\textbf{b.}

```{r}
mean_b1 <- mean(df$Birth_order1) 
mean_b2 <- mean(df$Birth_order2)

var_b1 <- var(df$Birth_order1)
var_b2 <- var(df$Birth_order2)

s_pooled <- ( 9*var_b1 + 9*var_b2 ) / (2*10-2)

lb <- (mean_b1-mean_b2) - qt(0.975, 18)*sqrt(s_pooled*(2/10))
up <- (mean_b1-mean_b2) + qt(0.975, 18)*sqrt(s_pooled*(2/10))
c(lb,ub)
```
\textbf{c.} 0 is in the $95\%$ confidence interval therefore we cannot reject the null hypothesis that the mean score does not depend on birth order. \newline

\section{2.35}
```{r}
form1 <- c(206, 193, 192, 188, 207, 210, 205, 185, 194, 187, 189, 178)
form2 <- c(177, 176, 198, 197, 185, 188, 206, 200, 189, 201, 197, 203)

mean_f1 <- mean(form1)
mean_f2 <- mean(form2)

var_f1 <- var(form1)
var_f2 <- var(form2)
n <- 12
```
\textbf{a.}
Observing all three plots we can see that the assumptions of normality and equal variance are incorrect. 

```{r}
qqnorm(form1, pch = 16, col='blue', main = "Formulation 1 Normal Q-Q Plot")
qqline(form1, lty=1)
qqnorm(form2, pch = 17, col='red', main = "Formulation 2 Normal Q-Q Plot")
qqline(form2, lty=3)

vlmts=range(form1,form2)
qqnorm(form1, ylim=vlmts, pch = 16, col='blue')
qqline(form1, lty=1)
par(new=T)
qqnorm(form2, ylim=vlmts, pch = 17, col='red')
qqline(form2, lty=3)
```
\textbf{b.}
The data do not support the claim that the mean deflection temperature under load for formulation 1 exceeds that of formulation 2. 
```{r}
a <- ((var_f1+var_f2)/n)^2
b <- (var_f1/n)^2/(n-1) + (var_f2/n)^2/(n-1)
degrees <- a/b

t <- (mean_f1-mean_f2)/sqrt((var_f1+var_f2)/n )
t
```
Rejection Region:
```{r}
qt(0.975, 22)
```
since $0.345 < 2.07$ we fail to reject the null.
\textbf{c.}
```{r}
pt(t, 22)
```
\newpage

\section{2.47}
```{r}
machine1 <- c(16.03, 16.01, 16.04, 15.96, 16.05, 15.98, 16.05, 16.02, 16.02, 15.99)
machine2 <- c(16.02, 16.03, 15.97, 16.04, 15.96, 16.02, 16.01, 16.01, 15.99, 16.00)

n <- 10

mean_m1 <- mean(machine1)
mean_m2 <- mean(machine2)

var_m1 <- var(machine1)
var_m2 <- var(machine2)
```
\textbf{a.}
$$H_0: \mu_1 - \mu_2 = 0$$
$$H_1: \mu_1 - \mu_2 \ne 0$$
\textbf{b.}
```{r}
s_pooled <- ( (n-1)*var_m1 + (n-1)*var_m2 )  / (2*n-2)
t <-  (mean_m1 - mean_m2) / sqrt(s_pooled*(2/n))
```
\textbf{c.}
```{r}
pt(t, 2*n-2)
```
\textbf{d.}
```{r}
d <- (mean_m1 - mean_m2) 
lb <- d - qt(0.975, 2*n-2)*sqrt(s_pooled*(2/n))
ub <- d + qt(0.975, 2*n-2)*sqrt(s_pooled*(2/n))
c(lb, ub)
```


