---
title: "Homework 3"
output: pdf_document
---

\begin{center}
Earle Aguilar \\
804501476 \\
01-27-2017
\end{center}

\section{3.4}

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l |}
    \hline
      Source  & DF & SS      & MS     & F     & P           \\ \hline
      Factor  & 4  & 987.71  & 246.93 & 33.10 & $\approx$ 0 \\ \hline
      Error   & 25 & 186.53  & 7.46   &       &             \\ \hline
      Total   & 29 & 1174.24 &        &       &             \\ \hline
  \end{tabular} 
\end{center}

\section{3.5}
No there are more than one type of chococalate that could have been tested. We could 
have tested combinations of those cholocate types and see their effects on depression. No, a causal effect cannot be established.  The study would have to include a random sample of people, not just individuals that already consume chocolate. There needs to be a control group that does not consume chocolate. The treatment group must be given a known quantity of chocolate.

\section{3.16}
```{r, echo = F}
Temp <- c(100, 100,100,100,100,125,125,125,125,
          150,150,150,150, 150 ,175,175,175,175)
Temp <- factor(Temp)
Density <- c(21.8 ,21.9 ,21.7 ,21.6 ,21.7,
             21.7 ,21.4 ,21.5, 21.4, 21.9, 
             21.8, 21.8, 21.6, 21.5, 21.9, 
             21.7, 21.8, 21.4)
RESI1 <- c(0.06 ,0.16 ,-0.04 ,-0.14 ,-0.04 ,
           0.2 ,-0.1 ,0 ,-0.1 ,0.18 ,
           0.08 ,0.08 ,-0.12 ,-0.22 ,
           0.2 ,0 ,0.1 ,-0.3)
p16 <- data.frame(Temp, Density, RESI1)
```
\subsection{a}
There are no signs that the temperature affects density. The p-value of the anova test is 0.1569.
```{r}
m1 <- lm(Density ~ Temp, p16)
anova(m1)
```
\subsection{b}
There is no indication that the temperature affects density therefore there is no need to use Fisher's LSD method.
\subsection{c}
There is no signs of non-constant variance in the residual plot.
```{r}
par(mfrow=c(2,2))
plot(m1)
```
\section{3.26}
```{r, echo=F}
Brand <- c(1 ,1 ,1 ,1 ,1, 2 ,2 ,2 ,2 ,2, 3 ,3 ,3 ,3 ,3)
Brand <- factor(Brand)
Life <- c(100 ,96 ,92 ,96 ,92, 76 ,80 ,75 ,84 ,82,
          108 ,100 ,96 ,98 ,100)
p26 <- data.frame(Brand, Life)
```
\subsection{a}
```{r}
m2 <- lm(Life ~ Brand, p26)
anova(m2)
```
The lives of the batteries are different. The p-value of the F-test produced by ANOVA is $6.141 \times 10^{-6}$
\subsection{b}
The residual plot shows that there is nothing wront. There is no trend line and the variance is constant.
```{r}
par(mfrow=c(2,2))
plot(m2)
```
\subsection{c}

\textbf{$95\%$ CI for Battery Brand 2}
```{r}
b <- p26[p26$Brand == 2,]
mean_b <- mean(b$Life)
sd_b <- sd(b$Life)
k <- qt(p = 0.975, 4)
se <- k * (sd_b/sqrt(5))
c(mean_b - se, mean_b +se)
```

\textbf{$99\%$ CI for Difference of Means}
```{r}
c <- p26[p26$Brand == 3,]
mean_c <- mean(c$Life)
sd_c <- sd(c$Life)
s_pooled <- (4*sd_c^2 + 4*sd_b^2) / 8
D <- mean_b - mean_c
t <- qt(0.99, 8)
se <- t* sqrt(s_pooled*(2/5))
c(D - se, D+se)
```
\subsection{d}
#TODO
\section{3.27}
```{r, echo=F}
Catalyst <- c(1 ,1 ,1 ,1 ,1 ,2 ,2 ,2 ,2 ,2,
              3 ,3 ,3 ,3 ,3 ,4 ,4 ,4 ,4 ,4)
Catalyst <- factor(Catalyst)
Concentration <- c(58.2 ,57.2 ,58.4 ,55.8 ,54.9,
                   56.3 ,54.5 ,57 ,55.3 ,0.0 ,50.1,
                   54.2 ,55.4 ,0.0 ,0.0 ,52.9 ,49.9 ,50 ,51.7, 0.0)
p27 <- data.frame(Catalyst, Concentration)
```
\subsection{a}
There is no evidence that suggest the catalysts have an effect on the concentration.
```{r}
m3 <- lm(Concentration ~ Catalyst, p27)
anova(m3)
```
\subsection{b}
There are signs of non constant variance.
```{r}
par(mfrow=c(2,2))
plot(m3)
```
\subsection{c}
```{r}
c1 <- p27[p27$Catalyst == 1,]
mean_c1 <- mean(c1$Concentration)
sd_c1 <- sd(c1$Concentration)
t <- qt(0.99, 4)
se <- t * (sd_c1/ sqrt(5))
c(mean_c1 - se, mean_c1 + se)
```
