---
title: "HW 4"
output: pdf_document
---


\section{3.32}
```{r}
wafer_pos <- c(1,1,1,2,2,2,3,3,3,4,4,4)
wafer_pos <- factor(wafer_pos)
uniformity <- c(2.76,5.67,4.49,1.43,1.7
               ,2.19,2.34,1.97,1.47,0.94
               ,1.36,1.65)
p16 <- data.frame(wafer_pos,uniformity)
```
\subsection{a}
There is significant difference in the treatments. The ANOVA table reports
a p-value of 0.007747.
```{r}
m1 <- lm(uniformity ~ wafer_pos, p16)
an1 <- anova(m1)
```
\subsection{b}
```{r}
sigma_t <- (an1$`Mean Sq`[1] -an1$`Mean Sq`[2])/ nrow(p16)
```
\subsection{c}
```{r}
ss_e <- an1$`Sum Sq`[2]
```
\subsection{d}
The errors are distributed normaly with exception of two points that could be 
outliers.

The residual plot shows signs of heteroskedasticity implying that constant variance
is being violated.
```{R}
qqnorm(m1$residuals)
qqline(m1$residuals)
```

```{r}
plot(m1,1:2)
```
\section{4.1}
\subsection{a}

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l |}
    \hline
      Source     & DF & SS      & MS     & F     & P                      \\ \hline
      Treatment  & 4  & 1010.56 & 252.64 & 29.84 & $3.75 \times 10^{-8}$  \\ \hline
      Block      & 5  & 323.82  & 64.765 & 7.65  & 0.000369               \\ \hline
      Error      & 20 & 169.33  & 8.47   &       &                        \\ \hline    
      Total      & 29 & 1503.71 &        &       &                        \\ \hline
  \end{tabular} 
\end{center}

\subsection{b}
6 Blocks.
\subsection{c}
There exists at least one treatment that is not the same.
\section{4.2}

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l |}
    \hline
      Source     & DF & SS      & MS     & F      & P                      \\ \hline
      Factor     & 4  & 907.71  & 246.93 & 33.10  & $1.47 \times 10^{-8}$  \\ \hline
      Block      & 5  & 80.00   & 16     &        &                        \\ \hline
      Error      & 20 & 186.53  & 7.46   &        &                        \\ \hline    
      Total      & 29 & 1174.24 &        &        &                        \\ \hline
  \end{tabular} 
\end{center}

\section{4.9}
```{r}
oil <- c(1,1,1,1,1,2,2,2,2,2,3,3,3,3,3)
oil <- factor(oil)
truck <- c(1,2,3,4,5,1,2,3,4,5,1,2,3,4,5)
truck <- factor(truck)
fuel_consumption <- c(0.5,0.634,0.487,0.329,0.512,
                      0.535,0.675,0.52,0.435,0.54,
                      0.513,0.595,0.488,0.4,0.51)
df <- data.frame(oil, truck, fuel_consumption)

```
\subsection{a}
```{r}
m2 <- lm(fuel_consumption ~ oil + truck, df)
an2 <-anova(m2)
```
\subsection{b}
Oils 1 and 2 differ and oils 2 and 3 differ from one another.
```{r}
mean_1 <- mean(df[df$oil == 1,3])
mean_2 <- mean(df[df$oil == 2,3])
mean_3 <- mean(df[df$oil == 3,3])

t_12 <- (mean_1 - mean_2) / sqrt(an2$`Mean Sq`[3] * (2/5))
t_13 <- (mean_1 - mean_3) / sqrt(an2$`Mean Sq`[3] * (2/5))
t_23 <- (mean_2 - mean_3) / sqrt(an2$`Mean Sq`[3] * (2/5))
```
\subsection{c}
```{r}
par(mfrow=c(2,2))
plot(m2, 1:2)
```
\section{4.12}
```{r}
project <- c(1,2,3,4,5,6,7,8,9,10,
             1,2,3,4,5,6,7,8,9,10,
             1,2,3,4,5,6,7,8,9,10)
project <- factor(project)
treatment <- c("MP Only","MP Only","MP Only","MP Only",
               "MP Only","MP Only","MP Only","MP Only",
               "MP Only","MP Only","MP + HDMTX","MP + HDMTX",
               "MP + HDMTX","MP + HDMTX","MP + HDMTX","MP + HDMTX",
               "MP + HDMTX","MP + HDMTX","MP + HDMTX","MP + HDMTX",
               "MP + LDMTX","MP + LDMTX","MP + LDMTX","MP + LDMTX",
               "MP + LDMTX","MP + LDMTX","MP + LDMTX","MP + LDMTX",
               "MP + LDMTX","MP + LDMTX")
treatment <- factor(treatment)
gene_Expression <- c(334.5,31.6,701,41.2,61.2,
                     69.6,67.5,66.6,120.7,881.9,
                     919.4,404.2,1024.8,54.1,62.8,
                     671.6,882.1,354.2,321.9,91.1,
                     108.4,26.1,240.8,191.1,69.7,
                     242.8,62.7,396.9,23.6,290.4)  
p4.12 <- data.frame(project, treatment, gene_Expression)
```
\subsection{a}
The ANOVA table has a p-value of 0.04568 for treatments indicating that there
is variation withing the treatments.
```{r}
m3 <- lm(gene_Expression ~ treatment + project, p4.12)
anova(m3)
```
\subsection{b}
The errors seem to be normaly distributed as shown in the normal proabability plot.
```{r}
qqnorm(m3$residuals)
qqline(m3$residuals)
```
\subsection{c}
Taking the log of the gene expression shows that there is no evidence that 
the treatments differ.
```{r}
p4.12$l.gene_Expression <- log(p4.12$gene_Expression)
m4 <- lm(l.gene_Expression ~ treatment + project, p4.12)
anova(m4)
```
\subsection{d}
The residual plot has a trend line indicating lack of fit for the data. The qq-norm plot shows data is not following normal distribution.
```{r}
par(mfrow=c(2,2))
plot(m4, 1:2)
```